A comparison between the latest Prophet forecasting model and the ARIMA model: An evaluation of BTC/ZAR predictability

### 2017-11-06 Draft/Write-up/Draft.tex
Final Paper

\begin{abstract}
The Autoregressive Integrated Moving Average (ARIMA) model is one of the
most widely used time series models that has gained popularity in the
exchange rate market due to its ease of implementation and tractability.
With the evolution of computational power, soft computing techniques
have since been used in exchange rate markets. The ARIMA model has been
used as the standard benchmark model against which these complex methods
have been compared. Although they have produced significantly better
results than the ARIMA model, these models lack interpretability and
building them is a challenging task. Prophet is a sophisticated model
that differs from traditional time series models in that it can be
utilised by non-experts who have little knowledge about the statistical
intricacies involved in the model, however have domain knowledge about
the data generating process. Prophet is also robust to outliers and can
handle missing values in the time series without the need for
interpolation. This paper compares the out-of-sample forecasts of
Prophet and ARIMA over varying forecast horizons, using a
Mincer-Zarnowitz approach for forecast evaluation. A complete dataset of
the prices of Bitcoin/Rand as well as a dataset which has missing prices
and outliers present is used in the analysis. It is found that the ARIMA
model produces the most efficient and unbiased forecasts over all
forecast horizons, and that the ARIMA model is more robust when faced
with missing values and outliers present in the data.
\noindent\\
Keywords: Prophet, ARIMA, Mincer-Zarnowitz,   Box-Jenkins, Bitcoin, Model Confidence Set
\end{abstract}
\end{titlepage}

@@

The Autoregressive Integrated Moving Average (ARIMA) model is one of the
most widely used time series models that have attracted attention in
financial market forecasting (Khashei, Bijari, and Ardali 2009).
Although the Random Walk model has typically been applied to foreign
exchange markets and has produced superior results, some researchers
have contended that foreign exchange markets are not efficient and
believe that future prices depend on current and past events
(Abu-Mostafa and Atiya 1996). This has led to the application of the
ARIMA model to exchange rate problems, where it has since gained
popularity due to its ease of implementation and tractability. The ARIMA
model is easy to use and yields good forecasts over short forecast
horizons, however the linearity of the ARIMA model fails to adequately
capture the non-linearity inherent in exchange rate data (Zhang and Hu
1998).

@@

In December 2016, Facebook open-sourced their forecasting model Prophet.
Prophet differs from traditional time series model such as the ARIMA in
that it can produce high quality forecasts in a straightforward way.
Prophet is a sophisticated model that provides informative results,
however is configurable and easy to use. It can be utilised by
non-experts who have little knowledge about the statistical intricacies
involved in the model, however have domain knowledge about the data
generating process. This knowledge can easily be incorporated into the
model through its intuitively adjustable parameters (Taylor and Letham
2017). Furthermore, Prophet is robust to outliers and can handle missing
values in the time series without the need for interpolation (Taylor and
Letham 2017). This allows analysts without knowledge on how to
pre-process the data, to utilise the model without sacrificing
predictive accuracy. If Prophet produces forecasts that are as good as
the ARIMA model, it can be compared to more complex forecasting methods
that are less tractable and flexible.

@@

Generalised autoregressive conditional heteroskedasticity (GARCH) models
were later developed due to the failure of ARIMA models to capture the
volatility in financial markets (Anastasakis and Mort 2009). Fahimifard
et al. (2009) applied a GARCH model to the Rial/USD and Rial/EUR to
compare the forecasts yielded by the GARCH and ARIMA model over varying
forecast horizons. Their results illustrated that the GARCH model
outperformed the ARIMA model when using the Root Mean Square Error
(RMSE), Mean Square Error (MSE) and Mean Absolute Deviation (MAD) as a
performance criteria.

@@

The techniques that have been considered for exchange rate forecasting
thus far, require the analyst to have vocational knowledge about time
series. Prophet differs from traditional time series models in that it
is flexible and can be customised by a large number of non-experts who
have little knowledge about time series, however have domain knowledge
about the data generating process. Prophet allows for a large number of
forecasts to be produced across a variety of problems and consists of a
robust evaluation system that allows for a large number of forecasts be
evaluated and compared. This is Facebook's definition of forecasting at
scale.

Prophet's Bayesian approach to forecasting allows the analyst to
incorporate their expert knowledge into the model building process and
has produced significantly improved forecasts compared to the ARIMA
model. Taylor and Letham (2017) forecasted the number of events on
Facebook using Prophet. The time series was impacted by holidays, had
strong multi-period seasonality, and a piecewise trend. The forecasts
produced by Prophet were compared to common forecasting techniques such
as exponential smoothing, ARIMA, the seasonal naive, and the naive
model. While exponential smoothing and the seasonal naive model were
quite robust, the ARIMA forecasts were fragile. No model besides Prophet
accounted for the dips around holidays and the upward trend of the time
series towards later observations. If Prophet produces forecasts that
are as good as the ARIMA model when forecasting BTC/ZAR, it can be
compared to more complex forecasting methods that are less tractable
such as the hybrid models and machine learning techniques seen earlier.

@@

Prophet's ability to forecast at scale enables it to model a wide
variety of data and may be able to adequately fit exchange rate data.
Its non-linear components could capture the non-linearity present in
exchange rates. In contrast, the ARIMA model is a linear function of
previous observations and lagged residuals and fails to capture the
non-linearity inherent in exchange rate data. Prophet performs well on
data with strong multiple ``human scale'' seasonalities and historical
trend changes. This differs to the ARIMA model which requires the data
to be de-trended and the variance stabilised before the model can be
fitted. Hence Prophet could model the weekly seasonality of closing
prices due to low trading activity which occurs around the weekend and
high trading activity which occurs mid-week.

@@

In this paper, the out-of-sample forecasts of ARIMA and Prophet are
compared over varying forecast horizons. The data is first split into a
training set and test set. The training set starts on the 24th January
2016 and ends on the 16th January 2017, while the test set starts on the
17th January 2017 and ends on the 17th July 2017. The Box-Jenkins
methodology is then used to select the correct ARIMA model while
Prophet's semi-automatic procedure is used for model selection. The
selected ARIMA and Prophet model are then fitted to the training set and
rolling window forecasts are made 1 day, 30 days and 90 days ahead. This
allows us to examine the forecast horizon effect. The Model Confidence
Set and Mincer-Zarnowitz test is then used to evaluate the forecasts
produced by ARIMA and Prophet against the test set. Since there is no
consensus on which accuracy statistic best measures the performance of
forecasting techniques, the most popular criteria, the Root Mean Squared
Error (RMSE) is employed. The results obtained from the ARIMA model will
be used as a benchmark for comparison. This process is then repeated
based on data which has outliers and missing values present.

@@

This paper makes use of Prophet's default settings to fit the data,
however weekly seasonality is included in the model. This allows us to
account for our prior knowledge about the closing prices of Bitcoin
which tend to be lower around the weekend however higher mid-week due to
fluctuations in trading activity. Furthermore, a linear trend is
appropriate since Bitcoin does not have an upper limit on its closing
prices.

@@

The Model Confidence Set (MCS) procedure developed by Hansen, Lunde, and
Nason (2011) is a sequential procedure which starts with an initial set
of models \(M_0\) of size m. The worst model is then eliminated at each
step until the null hypothesis of equal predictive ability (EPA) fails
to be rejected for all the models belonging to the set at a given
confidence level \(1 - \alpha\). This smaller set of models \(M^*\) is
the superior set of models (SSM) with the best case occurring when the
SSM consists of a single best model.

@@

\[t_i,_j = \frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\]
\vspace{1pt} \[ T_R = \max_{i,j\in M} \;\; |t_i,_j|\] where
\(\bar{d_i,_j} = m^{-1}\sum_{t=1}^{m}{d_i,_j,_t }\) measures the sample
average loss differential between model \(i\) and \(j\) and
\(\hat{var[\bar{d_i,_j}]}\) is estimated through bootstrapping as
described in Hansen, Lunde, and Nason (2011).

This paper uses a block--bootstrap procedure of 5000 resamples as in
Hansen, Lunde, and Nason (2011). The block length \(p\) is chosen by
fitting an AR(p) model to the \(d_i,_j,_t\) terms and determining the
maximum number of significant AR parameters obtained. While \(t_i,_j\)
has a t-distribution, \(T_R\) has a non-standard distribution under the
null hypothesis hence is estimated by implementing a bootstrapping
procedure similar to that used to estimate \(\hat{var[\bar{d_i,_j}]}\).

The worst model is then eliminated according to an elimination rule
which is coherent with the calculated t-statistic and is defined as:

\[e_R = \arg max_{i}\bigg(\sup_{j\in M}\frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\bigg)\]

\subsection{Mincer-Zarnowitz Approach to Forecast
Evaluation}\label{mincer-zarnowitz-approach-to-forecast-evaluation}

The Mincer-Zarnowitz approach to evaluating forecast accuracy is
commonly used and can be useful when comparing the forecasts produced by
Prophet and the ARIMA model. Mincer and Zarnowitz (1969) proposed an
absolute measure to evaluate forecast accuracy that considers the
distance between the actual and predicted values. To analyse the
absolute errors produced by the forecasts, the observed values \(r_t\)
are regressed against the predicted values \(\hat{r_t}\), i.e.
\[r_t = \alpha + \beta\cdot\hat{r_t} + e_t\] where \(\alpha\) represents
the mean distance between the observed and predicted values while
\(\beta\) represents the correlation between the forecasted errors and
predicted values. When \(\alpha = 0\) it implies that the forecasts are
unbiased and do not systematically overestimate or underestimate the
data. When \(\beta = 1\) it implies that the forecasts are efficient and
uncorrelated with the forecasted errors. A joint hypothesis test of
\(H_0: \alpha = 0 \cup \beta = 1\) is performed to check the efficiency
and bias of the forecasts and the model which produces the best results
generates superior forecasts.

@@

The original dataset is modified in order to examine how robust the
ARIMA and Prophet model are when faced with missing values and outliers.
20 values are randomly removed from the training set and 5 outliers are
randomly inserted in place of existing values. Both models are then
fitted to this ``dirty'' dataset and the forecasts are evaluated in the
same way as the ``clean'' dataset.

@@

We notice that a positive intercept and negative slope is still
estimated at the 1 day and 1 month forecast horizon when the data is
dirty. The intercept estimates are larger than the case of the clean
data, suggesting that the biasness of the forecasts yielded by both
models increases when there are outliers and missing values present in
the data. Contrary to the results from the clean data, Prophet's
intercept estimate lies closer to zero at the 1 month and 3 month
forecast horizon. This indicates that the mean forecasted returns
yielded by Prophet is closer to the mean observed returns when outliers
and missing values are present in the data. The negative intercept and
positive slope estimated for the 3 month horizon contrasts with the
positive intercept and negative slope estimated in the case of the clean
data. This shows that although the forecasts produced by both models are
systematically overestimated at long forecast horizons when the data is
dirty, they are no longer the opposite of the observed returns.

@@

The results show a clear difference in the predictive accuracy of the
ARIMA and Prophet model in addition to the forecast horizon effect. The
ARIMA model ranks ahead of Prophet when forecasting the returns of
BTC/ZAR across all forecast horizons. These results hold true
irrespective of whether there are missing values and outliers present in
the data. Nevertheless, it is reassuring to see that both models have
equal predictive accuracy when forecasting at short and long forecast
horizons when the data is clean and at short forecast horizons when the
data is dirty. Furthermore, the Mincer-Zarnowitz p-values for both
models are significant at the same forecast horizons, suggesting that
the efficiency and biasness of the return forecasts yielded by ARIMA and
Prophet are synchronized at each forecast horizon. Hence, if the analyst
is engaged in short-term or long-term trading, they could choose to
employ the Prophet model instead of the ARIMA model. This would allow
them to produce return forecasts that are as good as the ARIMA model,
without having any expert knowledge about model building and selection.
It would also provide them with the flexibility to customise the model
to suit their needs and incorporate their domain knowledge about BTC/ZAR
through the model's intuitively adjustable parameters. If the analyst is
interested in generating unbiased and/or efficient forecasts with the
least amount of forecast error, they could utilise either model, however
should only forecast BTC/ZAR returns over long forecast horizons with
data that do not include any outliers or missing values.

@@

Although the Prophet model was eliminated from the Model Confidence Set
at other forecast horizons, these results might change as more data and
information about events which might impact the price of BTC/ZAR becomes
available and is incorporated into the Prophet model. Furthermore, the
RMSE shows that the difference between the forecast errors of ARIMA and
Prophet is marginal, even in the case where both models don't have equal
predictive accuracy. Hence, if the analyst is willing to sacrifice a
small amount of predictive accuracy in return for the tractability and
ease of implementation which Prophet provides, then they might favour
Prophet over the ARIMA model.

>>>>

\begin{abstract}
The Autoregressive Integrated Moving Average (ARIMA) model is one of the
most widely used time series models that has gained popularity in the
exchange rate market due to its ease of implementation and tractability.
With the evolution of computational power, soft computing techniques
have since been used in exchange rate markets. The ARIMA model has been
used as the standard benchmark model against which these complex methods
have been compared. Although they have produced significantly better
results than the ARIMA model, these models lack interpretability and
building them is a challenging task. Prophet is a sophisticated model
that differs from traditional time series models in that it can be
utilised by non-experts who have little knowledge about the statistical
intricacies involved in the model, however have domain knowledge about
the data generating process. Prophet is also robust to outliers and can
handle missing values in the time series without the need for
interpolation. This paper compares the out-of-sample forecasts of
Prophet and ARIMA over varying forecast horizons, using the Model
Confidence Set and Mincer-Zarnowitz test to evaluate forecast accuracy.
A complete dataset of the prices of Bitcoin/Rand as well as a dataset
which has missing prices and outliers present is used in the analysis.
It is found that the ARIMA model ranks ahead of Prophet over all
forecast horizons and is more robust when faced with missing values and
outliers. In addition, both models having equal predictive accuracy when
forecasting at short and long forecast horizons when the data is clean
and at short forecast horizons when the data is dirty, with unbiased
and/or efficient forecasts only generated over the longest forecast
horizon in the case of the clean data.
\noindent\\
Keywords: Prophet, ARIMA, Mincer-Zarnowitz,   Box-Jenkins, Bitcoin, Model Confidence Set
\end{abstract}
\end{titlepage}

@@

The Autoregressive Integrated Moving Average (ARIMA) model is one of the
most widely used time series models that has attracted attention in
financial market forecasting (Khashei, Bijari, and Ardali 2009).
Although the Random Walk model has typically been applied to foreign
exchange markets and has produced superior results, some researchers
have contended that foreign exchange markets are not efficient and
believe that future prices depend on current and past events
(Abu-Mostafa and Atiya 1996). This has led to the application of the
ARIMA model to exchange rate problems, where it has since gained
popularity due to its ease of implementation and tractability. The ARIMA
model is easy to use and yields good forecasts over short forecast
horizons, however the linearity of the ARIMA model fails to adequately
capture the non-linearity inherent in exchange rate data (Zhang and Hu
1998).

@@

In December 2016, Facebook open-sourced their forecasting model Prophet.
Prophet differs from traditional time series models such as the ARIMA in
that it can produce high quality forecasts in a straightforward way.
Prophet is a sophisticated model that provides informative results,
however is configurable and easy to use. It can be utilised by
non-experts who have little knowledge about the statistical intricacies
involved in the model, however have domain knowledge about the data
generating process. This knowledge can easily be incorporated into the
model through its intuitively adjustable parameters (Taylor and Letham
2017). Furthermore, Prophet is robust to outliers and can handle missing
values in the time series without the need for interpolation (Taylor and
Letham 2017). This allows analysts without knowledge on how to
pre-process the data, to utilise the model without sacrificing
predictive accuracy. If Prophet produces forecasts that are as good as
the ARIMA model, it can be compared to more complex forecasting methods
that are less tractable and flexible.

@@

Generalised autoregressive conditional heteroskedasticity (GARCH) models
were later developed due to the failure of ARIMA models to capture the
volatility in financial markets (Anastasakis and Mort 2009). Fahimifard
et al. (2009) applied a GARCH model to the Rial/USD and Rial/EUR to
compare the forecasts yielded by the GARCH and ARIMA model over varying
forecast horizons. Their results illustrated that the GARCH model
outperformed the ARIMA model when using the Root Mean Square Error
(RMSE), Mean Square Error (MSE) and Mean Absolute Deviation (MAD) as
performance criteria.

@@

The techniques that have been considered for exchange rate forecasting
thus far, require the analyst to have vocational knowledge about time
series. Prophet differs from traditional time series models in that it
is flexible and can be customised by a large number of non-experts who
have little knowledge about time series, however have domain knowledge
about the data generating process. Prophet allows for a large number of
forecasts to be produced across a variety of problems and consists of a
robust evaluation system that allows for a large number of forecasts be
evaluated and compared. This is Facebookâs definition of forecasting
at scale.

Prophetâs Bayesian approach to forecasting allows the analyst to
incorporate their expert knowledge into the model building process and
has produced significantly improved forecasts compared to the ARIMA
model. Taylor and Letham (2017) forecasted the number of events on
Facebook using Prophet. The time series was impacted by holidays, had
strong multi-period seasonality, and a piecewise trend. The forecasts
produced by Prophet were compared to common forecasting techniques such
as exponential smoothing, ARIMA, the seasonal naive, and the naive
model. While exponential smoothing and the seasonal naive model were
quite robust, the ARIMA forecasts were fragile. No model besides Prophet
accounted for the dips around holidays and the upward trend of the time
series towards later observations. If Prophet produces forecasts that
are as good as the ARIMA model when forecasting BTC/ZAR, it can be
compared to more complex forecasting methods that are less tractable
such as the hybrid models and machine learning techniques seen earlier.

@@

Prophetâs ability to forecast at scale enables it to model a wide
variety of data and may be able to adequately fit exchange rate data.
Its non-linear components could capture the non-linearity present in
exchange rates. In contrast, the ARIMA model is a linear function of
previous observations and lagged residuals and fails to capture the
non-linearity inherent in exchange rate data. Prophet performs well on
data with strong multiple âhuman scaleâ seasonalities and historical
trend changes. This differs to the ARIMA model which requires the data
to be de-trended and the variance stabilised before the model can be
fitted. Hence Prophet could model the weekly seasonality of closing
prices due to low trading activity which occurs around the weekend and
high trading activity which occurs mid-week.

@@

In this paper, the out-of-sample forecasts of ARIMA and Prophet are
compared over varying forecast horizons. The data is first split into a
training set and test set. The training set starts on the 24th January
2016 and ends on the 16th January 2017, while the test set starts on the
17th January 2017 and ends on the 17th July 2017. The Box-Jenkins
methodology is then used to select the correct ARIMA model while
Prophetâs semi-automatic procedure is used for model selection. The
selected ARIMA and Prophet model are then fitted to the training set and
rolling window forecasts are made 1 day, 30 days and 90 days ahead. This
allows us to examine the forecast horizon effect. The Model Confidence
Set and Mincer-Zarnowitz test is then used to evaluate the forecasts
produced by ARIMA and Prophet against the test set. Since there is no
consensus on which accuracy statistic best measures the performance of
forecasting techniques, the most popular criteria, the Root Mean Squared
Error (RMSE) is employed. The results obtained from the ARIMA model will
be used as a benchmark for comparison. This process is then repeated
based on data which has outliers and missing values present.

@@

This paper makes use of Prophetâs default settings to fit the data,
however weekly seasonality is included in the model. This allows us to
account for our prior knowledge about the closing prices of Bitcoin
which tend to be lower around the weekend however higher mid-week due to
fluctuations in trading activity. Furthermore, a linear trend is
appropriate since Bitcoin does not have an upper limit on its closing
prices.

@@

The Model Confidence Set (MCS) for a set of models is analogous to a
confidence interval for a model parameter. The MCS procedure developed
by Hansen, Lunde, and Nason (2011) is a sequential procedure that starts
with an initial set of models \(M_0\) of size m. The worst model is then
eliminated at each step until the null hypothesis of equal predictive
ability (EPA) fails to be rejected for all the models belonging to the
set at a given confidence level \(1 - \alpha\). This smaller set of
models \(M^*\) is the superior set of models (SSM) with the best case
occurring when the SSM consists of a single best model.

@@

\[t_i,_j = \frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\]
\vspace{1pt} \[ T_R = \max_{i,j\in M} \;\; |t_i,_j|\] where
\(\bar{d_i,_j} = m^{-1}\sum_{t=1}^{m}{d_i,_j,_t }\) measures the sample
average loss differential between model \(i\) and \(j\) and
\(\hat{var[\bar{d_i,_j}]}\) is estimated through the bootstrapping
procedure described in Hansen, Lunde, and Nason (2011).

This paper uses a block-bootstrap procedure of 5000 resamples. The block
length \(p\) is chosen by fitting an AR(p) model to the \(d_i,_j,_t\)
terms and determining the maximum number of significant AR parameters
obtained. While \(t_i,_j\) has a t-distribution, \(T_R\) has a
non-standard asymptotic distribution under the null hypothesis hence is
estimated by implementing a bootstrapping procedure similar to that used
to estimate \({var[\bar{d_i,_j}]}\).

The worst model is then eliminated according to an elimination rule that
is coherent with the calculated t-statistic and is defined as:

\[e_R = \arg max_{i}\bigg(\sup_{j\in M}\frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\bigg)\]
\#\# Mincer-Zarnowitz Approach to Forecast Evaluation The
Mincer-Zarnowitz approach to evaluating forecast accuracy is commonly
used and can be useful when comparing the forecasts produced by Prophet
and the ARIMA model. Mincer and Zarnowitz (1969) proposed an absolute
measure to evaluate forecast accuracy that considers the distance
between the actual and predicted values. To analyse the absolute errors
produced by the forecasts, the observed values \(r_t\) are regressed
against the predicted values \(\hat{r_t}\), i.e.
\[r_t = \alpha + \beta\cdot\hat{r_t} + e_t\] where \(\alpha\) represents
the mean distance between the observed and predicted values while
\(\beta\) represents the correlation between the forecasted errors and
predicted values. When \(\alpha = 0\) it implies that the forecasts are
unbiased and do not systematically overestimate or underestimate the
data. When \(\beta = 1\) it implies that the forecasts are efficient and
uncorrelated with the forecasted errors. A joint hypothesis test of
\(H_0: \alpha = 0 \cup \beta = 1\) is performed to check the efficiency
and bias of the forecasts and the model which produces the best results
generates superior forecasts.

@@

The original dataset is modified in order to examine how robust the
ARIMA and Prophet model are when faced with missing values and outliers.
20 values are randomly removed from the training set and 5 outliers are
randomly inserted in place of existing values. Both models are then
fitted to this âdirtyâ dataset and the forecasts are evaluated in
the same way as the ``clean'' dataset.

@@

We notice that a positive intercept and negative slope is still
estimated at the 1 day and 1 month forecast horizon when the data is
dirty. The intercept estimates are larger than the case of the clean
data, suggesting that the biasness of the forecasts yielded by both
models increases when there are outliers and missing values present in
the data. Contrary to the results from the clean data, Prophetâs
intercept estimate lies closer to zero at the 1 month and 3 month
forecast horizon. This indicates that the mean forecasted returns
yielded by Prophet is closer to the mean observed returns when outliers
and missing values are present in the data. The negative intercept and
positive slope estimated for the 3 month horizon contrasts with the
positive intercept and negative slope estimated in the case of the clean
data. This shows that although the forecasts produced by both models are
systematically overestimated at long forecast horizons when the data is
dirty, they are no longer the opposite of the observed returns.

@@

The results show a clear difference in the predictive accuracy of the
ARIMA and Prophet model in addition to the forecast horizon effect. The
ARIMA model ranks ahead of Prophet when forecasting the returns of
BTC/ZAR across all forecast horizons. These results hold true
irrespective of whether there are missing values and outliers present in
the data. Nevertheless, it is reassuring to see that both models have
equal predictive accuracy when forecasting at short and long forecast
horizons when the data is clean and at short forecast horizons when the
data is dirty. Furthermore, the Mincer-Zarnowitz p-values for both
models are significant at the same forecast horizons, suggesting that
the efficiency and biasness of the return forecasts yielded by ARIMA and
Prophet are synchronized at each forecast horizon. Hence, if the analyst
is engaged in short-term or long-term trading, they could choose to
employ the Prophet model instead of the ARIMA model. This would allow
them to produce return forecasts that are as good as the ARIMA model,
without having any expert knowledge about model building and selection.
It would also provide them with the flexibility to customise the model
to suit their needs and incorporate their domain knowledge about BTC/ZAR
through the modelâs intuitively adjustable parameters. If the analyst
is interested in generating unbiased and/or efficient forecasts with the
least amount of forecast error, they could utilise either model, however
should only forecast BTC/ZAR returns over long forecast horizons with
data that do not include any outliers or missing values.

@@

Although the Prophet model was eliminated from the Model Confidence Set
at other forecast horizons, these results might change as more data and
information about events which might impact the price of BTC/ZAR becomes
available and is incorporated into the Prophet model. Furthermore, the
RMSE shows that the difference between the forecast errors of ARIMA and
Prophet is marginal, even in the case where both models donât have
equal predictive accuracy. Hence, if the analyst is willing to sacrifice
a small amount of predictive accuracy in return for the tractability and
ease of implementation which Prophet provides, then they might favour
Prophet over the ARIMA model.
